\tool{}: Specification- and Syntax-based Automated Testing Linguistic Capabilities of NLP Models

### 2023-01-10 paper/fse23/experiment.tex
fse23

\section{Experimental Setup}
\label{sec:experiment}
%
In this section, we present the setup of the experiments to evaluate
the effectiveness of \tool{}. We address the following research
questions (RQs):

\begin{enumerate}[label=\textbf{RQ\arabic*}]
\item \label{rq:three}: Can \tool generate more diverse test cases
  than \Cklst?
\item \label{rq:one}: Can \tool generate test sentences with correct sentiment labels?
\item \label{rq:two}: Are \tool generated test sentences correctly categorized into a \lc?
\item \label{rq:four}: Can \tool be useful to find root causes of bugs
  in the \sa models?
%% \item \label{rq:three}: How effective is our new test case generation
%%   using \cfg expansion? % ablation study
\end{enumerate}

@@

\paragraph{\textbf{NLP Models \& Dataset.}}
We evaluate our approach on three learning-based \sa models
implemented in Transformer library from the Hugging Face centralized
Model Hub:\footnote{https://huggingface.co/models} \texttt{\Bert}
(\bertsamodel), \texttt{\Roberta} (\robertasamodel), and \texttt{\Dbert} (\disbertsamodel). These models were pre-trained on English
language using a masked language modeling (MLM) objective, and
fine-tuned on the \sa task. In this experiment, we use \Sstt \cite{socher2013sst} dataset for
searching the seeds in \tool. \Sstt is a
corpus of movie review, and consists of 11,855 sentences
with sentiment scores. We split the
scores into ranges [0, 0.4], (0.4, 0.6] and (0.6, 1.0] to assign 
negative, neutral and positive labels, respectively. In addition, 
we use \Swn as the word sentiment dataset~\cite{baccianella2010sentiwordnet}. 
\Swn is a publicly available English sentiment lexicons.  
It provides lexical sentiment scores and the sentiment word labels 
are categorized by implementing the rules in~\cite{mihaela2017sentiwordnetlabel}.
%% \TODO{introduce details about each model}

\paragraph{\textbf{Comparison Baseline.}}
We compare \tool with
\Cklst,\footnote{https://github.com/marcotcr/checklist} a
manual template-based approach to generate test cases. In this
experiment, we used the \Cklst released \sa test cases which are
generated from its publicly available jupyter notebook implementation.
%% \TODO{introduce details about CHECKLIST}

@@

\paragraph{\textbf{RQ1.}}
Recall that a key limitation of \Cklst is that its template-based
approach relies on significant manual efforts and may not generate test cases that comprehensively cover the sentences
in a linguistic capability. \tool, instead, automatically generates test cases based on a search
dataset and the syntax in a large reference corpus. 
We expect \tool can generate a more diverse test suite than \Cklst, and achieve
more probable evaluation results.

We first evaluate the three \sa
models by testing them on the \tool generated test cases, reporting number of test cases and each model's failure rate in each linguistic capability.

Next,
to measure diversity, we follow the approach presented by Ma et al. \cite{ma2018deepgauge},
where the authors measure the coverage of NLP model intermediate states as corner-case neurons.
Because the matrix computation of intermediate states impacts NLP model decision-making, a test suite that covers a greater number of intermediate states can represent more NLP model decision-making, making it more diverse.
Specifically, we used two coverage metrics by Ma et al. \cite{ma2018deepgauge}, \textit{boundary coverage} (BoundCov) and \textit{strong activation coverage} (SActCov), to evaluate the test suite diversity.
It is worth noting that a test sample with a statistical distribution similar to the training data would rarely be found in the corner case region. As a result, covering a larger corner case region means that the test suite is more likely to be buggy.

@@

\noindent Equation \ref{eq:corner} shows the formal definition of the corner-case neuron of the NLP model $f(\cdot)$, where $\mathcal{X}$ is the given test suite, $N$ is the number of neurons in model $f(\cdot)$, $f_n(\cdot)$ is the $n^{th}$ neuron's output, and $high_n$ and $low_n$ are the $n^{th}$ neurons' output bounds on the model training dataset.
Eq. \ref{eq:corner} can be interpreted as the collection of neurons that emit outputs beyond the model's numerical boundary.

@@

\noindent The formal definition of our coverage metrics are shown in Equation \ref{eq:coverage}, where BoundCov measures the coverage of neurons that produce outputs that exceed the upper or lower bounds, and SActCov measures the coverage of neurons that create outputs that exceed the lower bound.
Higher coverage indicates the test suite is better for triggering the corner-case neurons, thus better test suite diversity.

@@

\paragraph{\textbf{RQ2 and RQ3}} As described in Section \ref{sec:approach},
\tool generates test cases in two steps: specification-based seed
generation and syntax-based sentence expansion. These automated steps
may generate seed/expanded sentences marked with incorrect sentiment
labels or categorized into wrong linguistic capabilities. For example,
the search rule and template defined in a linguistic capability may
not always generate seed sentences in that capability or with the
correct label.  To answer RQ2 and RQ3, we performed a manual study to
measure the correctness of the sentiment labels and linguistic
capabilities associated with the seed/expanded sentences, produced by
\tool.

In the manual study, we randomly sample 100 seed sentences, each of which has at least one expanded sentence, and divide these seeds to two sets (i.e., 50 in each set). For each sampled seed sentence, we randomly obtain one of its expanded sentences.
This forms the two sets of sentences (200 sentences in total) we use for this study, each with 50 seeds and 50 corresponding expanded sentences.
We recruited three participants of this study; all of them are graduate students with no knowledge about this work. 
2 of them were assigned one set of sentences and the third was assigned the other set.
Each participant was asked to provide two scores for each sentence.
\emph{(1) Relevancy score between sentence and its associated \lc}:
this score measures the correctness of \tool linguistic capability categorization.  The scores are discrete,
ranging from 1 (``strongly not relevant'') to 5 (``strongly relevant''). \emph{(2) sentiment score of the sentence}: this score measures the sentiment level of the sentence . It
is also discrete, ranging from 1 (``strongly
negative'') to 5 (``strongly positive''). 
We measure the following:

\begin{eqnarray}
  sent\_consistency &= \frac{1}{\#Sample\cdot~}\cdot \sum_{i} \delta(label_{S^2LCT}=label_{human}) \label{metric:srel} \\
  LC\_relevancy_{AVG} &= \frac{1}{\#Sample\cdot~}\cdot\sum_{i} Norm(LC\_relevancy_i) \label{metric:lcrel}
\end{eqnarray}

Equation~\ref{metric:srel} represents the percentage of the test cases that \tool and the participants produce the same sentiment labels. High value of this metric indicates \tool generates test cases with correct labels. Equation~\ref{metric:lcrel} represents the average of the
normalized relevancy score between a sentence and its associated
\lc. Higher average score means indicates the linguistic capability categorization by \tool is correct. We answer RQ2 and RQ3 using the metrics defined by
Equation~\ref{metric:srel} and Equation~\ref{metric:lcrel},
respectively.

\paragraph{\textbf{RQ4.}}

To answer RQ4, we conduct experiments to demonstrate that \tool can help developers understand the bugs in the NLP models.
Recall that \tool generates test cases by mutating seed sentences (\eg by expanding one token in the seed input). Still, it is unclear why mutating one token will cause the model to produce misclassified results.
We seek to help developers understand why such mutation will result in the misclassification. 
Existing work \cite{simin2020denas, lemna, lime} has demonstrated that the ML model prediction is dominated by a minimal set of input features (\ie tokens in input sentences). Motivated by such intuition, we identify a minimal set of input tokens that dominate the model prediction.

Formally, given a input sentence $x = [tk_1, tk_2, \cdots, tk_n]$, and the NLP model under test $f(\cdot)$, our goal is to find a masking template $T = [t_1, t_2, \cdots, t_n]$, where $t_i$ is 0 or 1, representing masking the $i^{th}$ token (\ie $tk_i$) in $x$ or not.
The template $T$ can mask some tokens in $x$ with attribute tokens, and the masked input has a high probability of retaining the original prediction $x$, denoted as
\begin{equation}
    P(f(T(x)) = f(x)) \ge P_{thresh}
    \label{eq:prob}
\end{equation}
To create such a template $T$, we first compute the contribution score of each input token using an existing explainable ML technique \cite{lemna}. We then begin with the full mask template (\ie, all tokens are masked); such full mask template definitely does not satisfy Equation \ref{eq:prob}.
We then iteratively shift one position from mask to non-mask based on the order of each token's contribution score, until the template $T$ satisfies Equation \ref{eq:prob}.
Because we iterate the size of the mask, the generated template $T$ will keep the minimum number of tokens in $x$. Moreover, since the input $x$ is an incorrect prediction, the generated template $T$ is likely to produce misclassification (i.e., the probability to be misclassified is larger than $P_{thresh}$).

>>>>

\section{Experimental Setup}
\label{sec:experiment}
%
In this section, we present the setup of our experiments to evaluate
the effectiveness of \tool. We answer the following research
questions (RQs):

\begin{enumerate}[label=\textbf{RQ\arabic*}]
\item \label{rq:three}: \textbf{Test Case Diversity.} Can \tool generate more diverse test cases
  than \Cklst?
\item \label{rq:one}: \textbf{Test Oracle.}  Can \tool generate test sentences with correct sentiment labels?
\item \label{rq:two}: \textbf{Capability Testing.} Are \tool generated test sentences correctly categorized into a \lc?
% \item \label{rq:four}: \textbf{Usefulness of Test Inputs.} Can \tool be useful to find root causes of bugs
%   in the \sa models?
%% \item \label{rq:three}: How effective is our new test case generation
%%   using \cfg expansion? % ablation study
\end{enumerate}

@@

\paragraph*{\textbf{NLP Models \& Dataset}}
We evaluate our approach on three learning-based \sa models released from the Hugging Face centralized
model hub:\footnote{https://huggingface.co/models} \texttt{\Bert}
(\bertsamodel), \texttt{\Roberta} (\robertasamodel), and \texttt{\Dbert} (\disbertsamodel). These models were pre-trained on English
language using a masked language modeling (MLM) objective, and
were fine-tuned on the \sa task. In this experiment, we used the \Sstt \cite{socher2013sst} dataset for
searching the seeds in \tool. \Sstt is a
corpus of movie review, consisting of 11,855 sentences
with sentiment scores. We split the
scores into ranges [0, 0.4], (0.4, 0.6] and (0.6, 1.0] to assign them
negative, neutral and positive labels, respectively. In addition,
\Swn~\cite{baccianella2010sentiwordnet} is a publicly available dataset for English sentiment lexicons.  
It provides lexical sentiment scores and the sentiment word labels 
are categorized by implementing the rules.
We used \Swn as both the generation and the expansion domain knowledge as shown in Figure \ref{fig:overview}.

\paragraph*{\textbf{Comparison Baseline}}
We compared \tool with
\Cklst,\footnote{https://github.com/marcotcr/checklist} a
manual template and \lc based approach to generate test cases. In this evalaution, we used \Cklst's \sa test cases that are
generated from its publicly available Jupyter Notebook implementation.

@@

\paragraph*{\textbf{RQ1}}
Recall that \Cklst relies on significant manual efforts and may not generate comprehensive test cases in a linguistic capability. \tool, instead, automatically generates test cases based on a search
dataset and the syntax in a large reference corpus. 
We expect \tool can generate a more diverse test suite than \Cklst.

We first evaluate the three \sa models by testing them on the \tool  test cases, reporting number of test cases and each model's failure rate in each linguistic capability. Specifically, for each \lc, we randomly choose 50, 100 and 200 seeds , and expand test cases from these seeds. We selected subsets of seeds to be used for expansion because the syntax-based expansion phase may be expensive to run all the generated seeds. We tested the three models using both seed and expanded test cases. To account for the randomness in random seed selection, we repeated these experiments 3 times and report median number of test cases and each model's failure rate.

We use two metrics to compare the diversity between the \tool generated seeds and the \Cklst test cases.

\paragraph*{\selfbleu} We reuse the input diversity metric, 
called \selfbleu, that Zhu \etal introduced~\cite{zhu2018texygen}. \bleu evaluates the token-level similarity.
% Regarding that \selfbleu takes each sentence as hypothesis and rest in a collection of textual data as reference, we calculate \bleu scores for every pairs of hypothesis and each reference sentence.
The \selfbleu is defined as the average \bleu scores over all reference sentences.
% Since the \bleu score ranges from 0 as the least similar inputs to 1 as the most similar inputs,
A higher \selfbleu score indicates less diversity in the test suite. In the experiment, we collected 50, 100 and 200 randomly selected \tool seeds and reported the median \selfbleu score over three trials for each group of seeds.
% The median \selfbleu over 3 trials of the random collection of the 50, 100 and 200 seeds is defined as the final \selfbleu scores. For the comparison, \selfbleu scores of \Cklst test cases are calculated in the same manner.

\paragraph*{Production rule coverage.} We propose a new metric to evaluate the syntactic diversity of the generated test suite.
It is defined as the number of production rules used in a set of test sentences. In our experiments, we used the Berkeley Neural Parser~\cite{kitaev2018seedparser,kitaev2019seedparser} to parse and collect all the production covered in a set of test sentences.
We compared the \pdr between 50, 100 and 200 randomly selected \tool seeds and the \Cklst test cases.
% collect the  of 50, 100 and 200 randomly selected \tool seeds and \Cklst test cases by the Berkeley Neural Parse~\cite{kitaev2018seedparser,kitaev2019seedparser}. Next, we traverse the parse trees and the \pdr score is calculated as the number of the production rules for the 50, 100 and 200 selected \tool seeds and \Cklst test cases.

% ---

In addition,
we follow the approach presented by Ma et al. \cite{ma2018deepgauge},
where the authors measure the coverage of NLP model intermediate states as corner-case neurons.
Because the matrix computation of intermediate states impacts NLP model decision-making, a test suite that covers a greater number of intermediate states can represent more NLP model decision-making, making it more diverse.
Specifically, we used two coverage metrics by Ma et al. \cite{ma2018deepgauge}, \textit{boundary coverage} (BoundCov) and \textit{strong activation coverage} (SActCov), to evaluate the test suite diversity.
It is worth noting that a test sample with a statistical distribution similar to the training data is rarely found in the corner case region.
Thus, covering a larger corner case region indicates that the test suite is more likely to be buggy.

@@

\noindent Equation \ref{eq:corner} defines the corner-case neuron of the NLP model $f(\cdot)$, where $\mathcal{X}$ is the given test suite, $N$ is the number of neurons in model $f(\cdot)$, $f_n(\cdot)$ is the $n^{th}$ neuron's output, and $high_n$ and $low_n$ are the $n^{th}$ neurons' output bounds on the model training dataset.
Equation \ref{eq:corner} can be interpreted as the collection of neurons that emit outputs beyond the model's numerical boundary.

@@

\noindent The definition of our coverage metrics is shown in Equation \ref{eq:coverage}, where BoundCov measures the coverage of neurons that produces outputs exceeding the upper or lower bounds, and SActCov measures the coverage of neurons that creates outputs exceeding the lower bound.
Higher coverage indicates the test suite is better for triggering the corner-case neurons, thus better test suite diversity.

@@

\paragraph*{\textbf{RQ2 and RQ3}} As described in Section \ref{sec:approach},
\tool generates test cases in two steps: specification-based seed
generation and syntax-based sentence expansion. These automated steps
may generate seed/expanded sentences marked with incorrect sentiment
labels or categorized into wrong linguistic capabilities.
% For example,
% the search rule and template defined in a linguistic capability may
% not always generate seed sentences in that capability or with the
% correct label. 
To answer RQ2 and RQ3, we performed a manual study to
measure the correctness of the sentiment labels and linguistic
capabilities associated with the seed/expanded sentences, produced by
\tool.

In the manual study, we randomly sample 100 \tool seed sentences, each of which has at least one expanded sentence, and divide these seeds to two sets (i.e., 50 in each set). For each sampled seed sentence, we randomly obtain one of its expanded sentences.
This forms the two sets of sentences (200 sentences in total) we use for this study, each with 50 seeds and 50 corresponding expanded sentences.
We recruited three participants for this study; all of them are graduate students with no knowledge about this work. 
2 of them were assigned one set of sentences and the third was assigned the other set.
Each participant was asked to provide two scores for each sentence.
\emph{(1) Relevancy score between sentence and its associated \lc}:
this score measures the correctness of \tool linguistic capability categorization.  The scores are discrete,
ranging from 1 (``strongly not relevant'') to 5 (``strongly relevant''). \emph{(2) sentiment score of the sentence}: this score measures the sentiment level of the sentence . It
is also discrete, ranging from 1 (``strongly
negative'') to 5 (``strongly positive''). 
We measure the following:

\begin{equation}
\begin{aligned}
  Label\_consistency = &\frac{1}{\#Sample}\\
  &\cdot \sum_{i} \delta(label_{S^2LCT}=label_{human})\label{metric:srel}\\
\end{aligned}
\end{equation}
\begin{equation}
\begin{aligned}
  LC\_relevancy_{AVG} = &\frac{1}{\#Sample}\\
  &\cdot\sum_{i} Norm(LC\_relevancy_i) \label{metric:lcrel}
\end{aligned}
\end{equation}

Equation~\ref{metric:srel} represents the percentage of the test cases that \tool and the participants produce the same sentiment labels. High value of this metric indicates \tool generates test cases with correct labels. Equation~\ref{metric:lcrel} represents the average of the
normalized relevancy score between a sentence and its associated
\lc. The relevancy score is to evaluate the relevancy of the sentence to be used for testing model under test on the corresponding \lc. Higher average score means indicate the linguistic capability categorization by \tool is correct. We answer RQ2 and RQ3 using the metrics defined by
Equation~\ref{metric:srel} and Equation~\ref{metric:lcrel},
respectively.

### 2023-01-10 paper/fse23/intro.tex
fse23

\Nlp (NLP) applications are growing exponentially.  As a result,
trustworthiness in the quality of NLP applications has become critical
for its practical use in the real world.  Therefore, quality assurance
of NLP applications is essential in the software
development process.  
Researchers aim to improve the current practices of testing NLP models
from three perspectives: (i) \emph{test input generation}, (ii)
\emph{automated test oracle}, and (iii) \emph{meaningful quality
  metrics}.

\noindent \textbf{Test input generation.} Currently, most testing of
an NLP model uses existing, large textual corpus as the testing
dataset to evaluate the model. This practice often overestimates
the model performances from the \ho
dataset~\cite{patel2018mlevalforsoftware, recht2019imagenetbias,
  marcoACL2020checklist}.  The overestimation comes from the
discrepancy between the distribution of the used dataset and the actual data
distribution in real world. Oftentimes, the \ho dataset is not
representative and is likely to introduce specific biases, leading to the
decreased robustness of NLP models. In this regard, prior works
have proposed techniques for testing the robustness of NLP models by crafting
adversarial examples and attacking a model with them intentionally (i.e., adversarial testing)
\cite{ribeiro2018sear,belinkov2018breaknmt,
  rychalska2019wildnlp,iyyer2018adversarial}.

\noindent \textbf{Automated test oracle.} The current testing practice
requires manual efforts to label the test oracles of the \ho
data. The manual work is costly in terms of time consumption and its
impact on the market price. Therefore, it necessitates automated test
oracle generation for improving the testing process of NLP
models. 
% validity of the automation is ensured by the
% correctness of test oracle.
However, automatically generating test oracles may not always
be feasible; predicting the correct test oracles remains one of main
challenges. Along with this, motivated by software metamorphic testing 
approach~\cite{segura2016metamorphictest}, we address the challenge by specifying linguistic rules determined by input-output relations, and we only accept validated test oracles by the rules. 
% \TODO{Describe and Add citations to metamorphic testing techniques
%   here}\jl{done.}

%% \sw{Not sure what overestimate means here}
%  In addition, the inconsistency between test input and
% its oracle causes biases. Such biases increase the discrepancy of
% distribution between the dataset and real-world data.
\noindent \textbf{Meaningful quality metrics.}  
Traditionally, the quality of NLP models are
represented by numbers in quality metrics. Especially, accuracy (i.e., the fraction of outputs that the
model correctly predicts) is the most widely used metric for assessing
the quality of classification models. 
Generally, higher accuracy number suggests better quality of a model.
However, all NLP models have their strengths and weaknesses, and 
forcing aggregation statistics into a single number (i.e., accuracy) makes it difficult for the users to assess the capabilities of NLP models.  Not to
mention localizing and fixing the bugs found from the \ho
set (i.e., testing dataset, as opposed to training dataset). Therefore, this forced aggregation method not only fails to
validate the linguistic capability of the model, but it also makes the localization of the
causes of the inaccuracy more costly~\cite{wu2019errudite}.
% Therefore behavioral testing
% approach provides the better ability to examine the inaccuracy and
% find the bugs in the model.
To address this limitation,
% several approaches have been proposed to
% evaluate different aspects of the NLP models, such as , model coverage
% \cite{rottger2020hatecheck}, and fairness
% \cite{prabhakaran2019fairness,rottger2020hatecheck}. In addition, For example, Testing model coverage
% only shows model behaviors, but not the model performance on existing
% testing set. The fairness and robustness testing only focus on only
% one model capability resulting in its limited comprehensiveness. In
% addition,
Ribeiro~\etal introduced \Cklst, a behavioral testing framework for
evaluating NLP model on multiple linguistic
capabilities~\cite{marcoACL2020checklist}. \Cklst defines
task-relevant linguistic capabilities and generates test cases for
each \lc.

However, none of the above approaches satisfy all three requirements
at the same time. First, the adversarial testing approaches merely
focus on evaluating model robustness. They measure how sensitive the models
are to input perturbations while do not
evaluate linguistic functionalities.
Second, the metamorphic testing approach requires understanding the characteristics of metamorphic relations between inputs
and outputs. However, finding these remains one of the most challenging
problems~\cite{segura2016metamorphictest}. In addition, metamorphic
relation in textual data in the NLP domain has not been explored despite
its importance.
Third, \Cklst relies on manually generated input templates,
which need to be preset before test input generation. Consequently,
\Cklst templates are distributed in a limited range of their
structures. This restricts \Cklst's ability to comprehensively test
the linguistic capabilities.

Despite \Cklst's limitations, assessing the quality of NLP models
through the linguistic capabilities is a promising direction. Each \lc
explains the functionality of the input and output behavior for the
NLP model under test. Typically, it describes certain type of inputs
and outputs observed in real world for the target NLP task, ranging
from simple to complicated behaviors. Testing the linguistic capabilities allows the model developers to better understand the capabilities and potential issues of the NLP
models. For example, a linguistic capability of ``Negated neutral
should still be neutral'' measures how accurately the \sa model
understands that the negated neutral input has neutral sentiment
\cite{marcoACL2020checklist}, requiring the \sa model to
output neutral sentiment on the negated neutral inputs.  Such evaluation
methodology on the specified functionalities avoids the
overestimation of the model performance as it measures
the model performance on each functionality.
% ,and the separate model performance
% explain distribution of the performance over the linguistic capabilities
In the end, testing through linguistic capabilities provides not only
the overall model performance, but also the malfunction facets of the
model.

To satisfy all three requirements mentioned above, we present \tool,
an automated evaluation method for comprehensive behavioral
testing of NLP models on \sa task.  There are three main challenges
that \tool overcomes to satisfy all three aforementioned requirements.
\begin{description}
\item[{\bf C1}] The test suite should cover diverse syntactic structures;
\item[{\bf C2}] Each test case should be automatically categorized into a \lc;
\item[{\bf C3}] The label of each test case should be automatically
  and accurately defined.
\end{description}

\noindent \textbf{C1.} The first challenge comes with the second and third challenges of maintaining the linguistic capability and label of the test sentence while making the syntactic structure of the sentence diverse. 
To address this challenge, \tool establishes specifications for evaluating
a linguistic capability and searches suitable sentences that satisfy
the specification from existing public dataset. In this process, \tool
generates new inputs by mutating the searched sentences, used as seed
inputs. \tool expands the grammar structure of a seed input and determines its
available \pos to maintain structural naturalness.

@@

\noindent \textbf{C2.} Suitability of test sentences for evaluating NLP
model on a \lc is determined by its relevancy to the
\lc. Relevancy between a test sentence and its \lc is challenging to be maintained when transforming and expanding the test sentence.
This is because the \lc is defined on a specific 
mixture of syntax and semantics of the sentence, and there exists no automatic way to check the consistency of each sentence with the semantics specified in the corresponding \lc due to the inherent ambiguity of natural language sentences. To address this difficulty, \tool implements search rules
and the transformation templates of \lcs. In addition, it analyzes the parse
tree of the seed sentence to identify possible expansion.
%% \tool adopts behavioral model testing method by
%% introducing multiple behaviors from \lcs on \sa tasks and generating
%% inputs relevant to each \lc. Each test case provides not only
%% correctness of model prediction on it, but \lc on the test case also
%% gives information about classification on the model
%% performance. Therefore assigning appropriate \lc for each test case
%% alleviates overestimation of model testing results.

\noindent \textbf{C3.} Last challenge is on automated test oracle.  For NLP tasks, test oracle is
determined by understanding the meaning of texts. This requires domain knowledge of different NLP tasks.
% Therefore, generation of test case ought to ensure the
%correctness of its oracle allocation.
In this work, as a first step, we consider \sa as the NLP task for the models under test. \tool obtains the
appropriate test oracle by implementing domain-specific
knowledge on the word sentiment dataset and word suggestion model for validation of generated sentence and its oracle.

@@

\begin{itemize}[topsep=3pt,itemsep=3pt,partopsep=0ex,parsep=0ex,leftmargin=*]
\item We design and implement an automated testing tool, \tool, and compared it with \Cklst. We find that the test cases generated by \tool achieves higher coverage than \Cklst when used for testing sentiment analysis models.
%
\item We perform a manual study to
measure the correctness of the sentiment labels and their \lcs produced by \tool. We find that \tool generates test cases that consistently label their sentiment correctly as human understanding.
%
\item We analyze the root causes of the misclassification in the sentiment analysis models, guided by \tool testing result. We find that seed and expanded test cases, produced by \tool, are usefulness of \tool for understanding bugs in the models.
\end{itemize}

>>>>

\Nlp (NLP) applications are growing rapidly.  As a result,
trustworthiness in how the quality of NLP applications is assessed becomes critical
for its practical use in the real world.  
Traditionally, the quality of NLP models is
assessed using aggregated metrics. In particular, accuracy (i.e., the fraction of outputs that the
model correctly predicts) is the most widely used metric for assessing
the quality of classification models:
higher accuracy suggests better quality of a model.
However, all NLP models have their strengths and weaknesses; 
using a single, aggregated metric (i.e., accuracy) makes it difficult for the users to assess the capabilities of NLP models.
Such a metric fails to validate how well a model supports linguistic capabilities~\cite{geva2019we,gururangan2018annotation} (e.g., when the model always fails on certain type of inputs).
% Not to
% mention localizing and fixing the bugs found from the \ho
% set (i.e., testing dataset, as opposed to training dataset). Therefore, this forced aggregation method not only fails to
% validate the linguistic capability of the model, but it also makes the localization of the
% causes of the inaccuracy more costly~\cite{wu2019errudite}.

To address this limitation, methodologies to assess an NLP model on a set of
  linguistic capabilities have been introduced~\cite{marcoACL2020checklist,rottger2020hatecheck}. 
A \lc
explains a functionality of the input and output behavior for the
NLP model under test. Typically, it describes certain type of inputs
and outputs observed in real world for the target NLP task.
% , ranging
% from simple to complicated behaviors.
Testing the linguistic capabilities allows the model developers to better understand the capabilities and potential issues of the NLP
models. 
For example,  \Cklst~\cite{marcoACL2020checklist}, a behavioral testing framework for evaluating NLP models, defines a linguistic capability called ``Negated neutral should still be neutral'' to measure how accurately a \sa model understands that the negated neutral input has neutral sentiment
\cite{marcoACL2020checklist}. 
It requires the \sa model to
output neutral sentiment on the negated neutral inputs. 
Such evaluation methodology avoids the overestimation of the model performance as it measures the model performance on each functionality.
% ,and the separate model performance
% explain distribution of the performance over the linguistic capabilities
In the end, testing through linguistic capabilities provides not only the overall model performance, but also the malfunction facets of the model.

 However, existing linguistic capability-based testing approaches rely on manually generated input templates, which need to be preset before generating tests. 
 As a result, these templates are limited in their sentence
structures. This restricts existing approaches' ability to comprehensively test linguistic capabilities.

%  For example, \. \Cklst defines
% task-relevant linguistic capabilities and generates test cases for
% each \lc.

% Therefore, quality assurance
% of NLP applications is essential in the software
% development process.  
% Researchers aim to improve the current practices of testing NLP models
% from three perspectives: (i) \emph{test input generation}, (ii)
% \emph{automated test oracle}, and (iii) \emph{meaningful quality
%   metrics}.

% \noindent \textbf{Test input generation.} Currently, most testing of
% an NLP model uses existing, large textual corpus as the testing
% dataset to evaluate the model. This practice often overestimates
% the model performances from the \ho
% dataset~\cite{patel2018mlevalforsoftware, recht2019imagenetbias,
%   marcoACL2020checklist}.  The overestimation comes from the
% discrepancy between the distribution of the used dataset and the actual data
% distribution in real world. Oftentimes, the \ho dataset is not
% representative and is likely to introduce specific biases, leading to the
% decreased robustness of NLP models. In this regard, prior works
% have proposed techniques for testing the robustness of NLP models by crafting
% adversarial examples and attacking a model with them intentionally (i.e., adversarial testing)
% \cite{ribeiro2018sear,belinkov2018breaknmt,
%   rychalska2019wildnlp,iyyer2018adversarial}.

% \noindent \textbf{Automated test oracle.} The current testing practice
% requires manual efforts to label the test oracles of the \ho
% data. The manual work is costly in terms of time consumption and its
% impact on the market price. Therefore, it necessitates automated test
% oracle generation for improving the testing process of NLP
% models. 
% % validity of the automation is ensured by the
% % correctness of test oracle.
% However, automatically generating test oracles may not always
% be feasible; predicting the correct test oracles remains one of main
% challenges. Along with this, motivated by software metamorphic testing 
% approach~\cite{segura2016metamorphictest}, we address the challenge by specifying linguistic rules determined by input-output relations, and we only accept validated test oracles by the rules. 
% \TODO{Describe and Add citations to metamorphic testing techniques
%   here}\jl{done.}

%% \sw{Not sure what overestimate means here}
%  In addition, the inconsistency between test input and
% its oracle causes biases. Such biases increase the discrepancy of
% distribution between the dataset and real-world data.
% \noindent \textbf{Meaningful quality metrics.}

% Therefore behavioral testing
% approach provides the better ability to examine the inaccuracy and
% find the bugs in the model.

% several approaches have been proposed to
% evaluate different aspects of the NLP models, such as , model coverage
% \cite{rottger2020hatecheck}, and fairness
% \cite{prabhakaran2019fairness,rottger2020hatecheck}. In addition, For example, Testing model coverage
% only shows model behaviors, but not the model performance on existing
% testing set. The fairness and robustness testing only focus on only
% one model capability resulting in its limited comprehensiveness. In
% addition,

% However, none of the above approaches satisfy all three requirements
% at the same time. First, the adversarial testing approaches merely
% focus on evaluating model robustness. They measure how sensitive the models
% are to input perturbations while do not
% evaluate linguistic functionalities.
% Second, the metamorphic testing approach requires understanding the characteristics of metamorphic relations between inputs
% and outputs. However, finding these remains one of the most challenging
% problems~\cite{segura2016metamorphictest}. In addition, metamorphic
% relation in textual data in the NLP domain has not been explored despite
% its importance.
% Third,

% Despite \Cklst's limitations, assessing the quality of NLP models
% through the linguistic capabilities is a promising direction.

To address this issue, we present \tool,
an automated linguistic capability-based testing framework for NLP models.  
The goal of \tool is to generate a diverse linguistic capability-based test suite for a given model, both in terms of covering diverse linguistic structures and diverse model behaviors.
To achieve the goal, \tool needs to address two challenges.
\textit{(i) Capability-based Assessment.} Each test case should be automatically categorized into a \lc;
and \textit{(ii) Automated Test Oracle.} The label of each test case should be automatically
  and accurately defined.
% \end{description}

%\noindent \textbf{C1.} The first challenge comes with the second and third challenges of maintaining the linguistic capability and label of the test sentence while making the syntactic structure of the sentence diverse. To address this challenge, \tool establishes specifications for evaluating a linguistic capability and searches suitable sentences that satisfy the specification from existing public dataset. In this process, \tool generates new inputs by mutating the searched sentences, used as seed inputs. \tool expands the grammar structure of a seed input and determines its available \pos to maintain structural naturalness.

@@

\noindent \textbf{Capability-based Assessment.} The suitability of test sentences for evaluating NLP
models on a \lc is determined by its relevancy to this
\lc. It is challenging to maintain relevancy between a test sentence and its \lc when transforming and expanding the test sentence.
This is because the \lc is defined on a specific 
mixture of syntax and semantics of the sentence. Due to the inherent ambiguity of natural language sentences, there exists no automatic way to check the consistency of each sentence with the semantics specified in the corresponding \lc. To address this difficulty, \tool defines specifications (search rules
and transformation templates) of \lcs, and analyzes the parse
tree of the seed sentence to identify possible expansion.
%% \tool adopts behavioral model testing method by
%% introducing multiple behaviors from \lcs on \sa tasks and generating
%% inputs relevant to each \lc. Each test case provides not only
%% correctness of model prediction on it, but \lc on the test case also
%% gives information about classification on the model
%% performance. Therefore assigning appropriate \lc for each test case
%% alleviates overestimation of model testing results.

\noindent \textbf{Automated Test Oracle.}   For NLP model testing, test oracle is usually determined by understanding the semantics of texts and requires domain knowledge of different NLP tasks.
Thus, the current testing practice requires manual efforts to create the test oracles of the \ho data. The manual work is costly in terms of time consumption. Therefore, it necessitates automated test oracle generation for improving the testing process of NLP models. 
% % validity of the automation is ensured by the
% % correctness of test oracle.
 However, automatically generating the  test oracles remains one of the main challenges in NLP software testing~\cite{huang2022aeon}. 
 A few metamorphic testing approaches have been proposed in image recognition domain, but they require understanding the characteristics of metamorphic relations between inputs and outputs, which require domain expertise and non-trivial manual efforts ~\cite{segura2016metamorphictest}. In addition, it is even more challenging to design metamorphic relations in textual data because the semantics of nature language sentences can be greatly changed even by a slight perturbation to the sentences.
 %Along with this, motivated by software metamorphic testing approach~\cite{segura2016metamorphictest}, we address the challenge by specifying linguistic rules determined by input-output relations, and we only accept validated test oracles by the rules.

% Therefore, generation of test case ought to ensure the
%correctness of its oracle allocation.
In this work, as a first step, we consider \sa as the NLP task for the models under test. 
\tool obtains the
appropriate test oracle by implementing domain-specific
knowledge on the word sentiment dataset and word suggestion model for validating the generated sentence and its oracle.

@@

\begin{itemize}[topsep=3pt,itemsep=3pt,partopsep=0ex,parsep=0ex,leftmargin=*]
\item We design and implement an automated testing tool, \tool, and compared it with \Cklst. We find that the test cases generated by \tool achieve 100\% higher coverage than \Cklst when used for testing sentiment analysis models. 
%
\item We perform a manual study to
measure the correctness of the sentiment labels and their \lcs produced by \tool. We find that \tool generates test cases that consistently label their sentiment correctly as human.
%
\item We analyze the root causes of misclassification in the sentiment analysis models, guided by \tool testing result. We find that seeds and expanded test cases produced by \tool are rather useful in helping developers understand bugs in the model.
\end{itemize}
